\assignment

### 2017-03-19 project/paper.rnw
The quadrature scheme is too complicated.

<<packages, message = FALSE, cache = FALSE>>=
library(parallel)
library(spatstat)

set.seed(c(83534, 251, -18691, 283, -2526, 782), kind = 'L\'Ecuyer-CMRG')
@

@@

# Define the window for the UXO site.
sitewindow <- owin(poly = cbind(x = c(1564294, 1564495, 1556870, 1557126),
                                y = c(535421, 541130, 541085, 535576)))
@

In my writing project, I evaluated ordinary kriging of moving average
intensity values on a simulated tank training range. I will use the same site
for this project. The site is a
\Sexpr{sprintf('%.1f', area(sitewindow) / 43560)} acre quadrilateral region
with homogeneous Poisson process producing background anomalies with an
intensity of 100 anomalies per acre, and two regions of concentrated munitions
use generated as Poisson processes with bivariate Gaussian intensity. The
total intesnsity at the center of each concentrated munitions use region is
300 anomalies per acre~(Figure~\ref{fig:truth}).

<<truth, cache = TRUE, fig.width = 3.75, fig.pos = 't', fig.cap = 'True intensity at the simulated UXO site.'>>=
x <- seq(1556870, 1564495, by = 20)
y <- seq(535421, 541130, by = 20)
intense.mat <- matrix(100, nrow = length(x), length(y))
for(i in seq_along(x)){
  for(j in seq_along(y)){
    intense.mat[i, j] <- 100 + gauss.elliptic(x[i]+10, y[j]+10,
        mu.x = 1558400, mu.y = 540000,
        s.a = 800/(2*qnorm(0.995)), s.b = 1200/(2*qnorm(0.995)),
        r = pi/6, maxrate = 200
      ) + gauss.elliptic(x[i]+10, y[j]+10,
        mu.x = 1562000, mu.y = 537000,
        s.a = 2000/(2*qnorm(0.995)), s.b = 900/(2*qnorm(0.995)),
        r = 0, maxrate = 200
      )
  }
}
intense.im <- im(t(intense.mat), x+10, y+10, unitname = c('foot', 'feet'))

par(mar = c(0, 0, 1, 3))
plot(intense.im, main = 'True Intensity Surface', zlim = c(100, 300), las = 2)
plot(setminus.owin(owin(c(1556870, 1564495), c(535421, 541130)),
                   sitewindow), col = 'white', add = TRUE)
mtext('Anomalies per Acre', 4, line = 2)
@

easy site, realization 2,000, 390 ft spacing, 6 ft width

@@

>>>>

<<packages, message = FALSE, cache = FALSE>>=
library(spatstat)

set.seed(83534)
@

@@

# Define the window for the UXO site.
site_window <- owin(poly = cbind(x = c(1564294, 1564495, 1556870, 1557126),
                                 y = c(535421, 541130, 541085, 535576)))
@

In my writing project, I evaluated ordinary kriging of moving average
intensity values on a simulated tank training range. I will use the same site
for this project. The site is a
\Sexpr{sprintf('%.2f', area(site_window) / 43560)} acre quadrilateral region
with homogeneous Poisson process producing background anomalies with an
intensity of 100 anomalies per acre, and two regions of concentrated munitions
use generated as Poisson processes with bivariate Gaussian intensity. The
total intesnsity at the center of each concentrated munitions use region is
300 anomalies per acre~(Figure~\ref{fig:truth}).

<<truth, cache = TRUE, fig.width = 4, fig.pos = 't', fig.cap = 'True intensity at the simulated UXO site.'>>=
# Create an image of the surface in 20 ft by 20 ft pixels.
# The gauss.elliptic function from spatial_functions.r is a bivariate normal
# intensity parameterized in terms of the center, major and minor axis scales,
# and angle of the major axis.
x <- seq(1556880, 1564495, by = 20)
y <- seq(535431, 541130, by = 20)
intense.mat <- matrix(100, nrow = length(x), length(y))
for(i in seq_along(x)){
  for(j in seq_along(y)){
    intense.mat[i, j] <- 100 + gauss.elliptic(x[i], y[j],
        mu.x = 1558400, mu.y = 540000,
        s.a = 800 / (2 * qnorm(0.995)), s.b = 1200 / (2 * qnorm(0.995)),
        r = pi/6, maxrate = 200
      ) + gauss.elliptic(x[i], y[j],
        mu.x = 1562000, mu.y = 537000,
        s.a = 2000 / (2 * qnorm(0.995)), s.b = 900 / (2 * qnorm(0.995)),
        r = 0, maxrate = 200
      )
  }
}
intense.im <- im(t(intense.mat), x, y, unitname = c('foot', 'feet'))

par(mar = c(0, 0, 1, 3))
plot(intense.im, main = 'True Intensity Surface',
     border = NA, zlim = c(100, 300), las = 2)
plot(setminus.owin(owin(c(1556870, 1564495), c(535421, 541130)),
     site_window), col = 'white', border = 'white', lwd = 2, add = TRUE)
mtext('Anomalies per Acre', 4, line = 2)
@

<<sim2000obs, fig.pos = 't', fig.cap = 'Observed geomagnetic anomalies from one realization of the UXO site. The transects are not shown on this plot because they would obscure the points.'>>=
# Load the sample data used in my writing project.
# The anomaly file contains the locations of the observed anamolies and the
# cog file contains the course-over-ground waypoints on the transects.
ex_anom <- read.csv(file.path(vspuxo, 'datasets', 'easy', 'sample',
                    'easy_sample_tTA2_p200_bg100_fg200_rep2000.anomaly'))
ex_path <- read.csv(file.path(vspuxo, 'datasets', 'easy', 'sample',
                    'easy_sample_tTA2_p200_bg100_fg200_rep2000.cog'))

# Create a spatstat window and ppp object.
ex_win <- intersect.owin(site_window,
  do.call(union.owin, lapply(unique(ex_path$x), function(x){
    return(owin(c(x - 3, x + 3), c(535421, 541130)))
  })))
ex_ppp <- ppp(ex_anom$x, ex_anom$y, window = ex_win)

par(mar = c(0, 0, 1, 0))
plot(ex_ppp, main = 'Observed Geomagnetic Anomalies', pch = '.', border = NA)
plot(site_window, add = TRUE)
@

I simulate data collection along parallel straight-line transects spaced 396
feet apart using a detector with a footprint six feet wide (so there is an
unobserved region 390 feet wide between each pair of adjacent transects). The
location of the first transect is selected randomly, and the locations of all
anomalies within three feet of a transect are
recorded~(Figure~\ref{fig:sim2000obs}). In total,
\Sexpr{sprintf('%.1f', area(ex_win) / 43560)} acres are observed, covering
\Sexpr{sprintf('%.1f\\%%', 100 * area(ex_win) / area(site_window))} of the
qegion of interest.

@@

<<polyfit1, eval = FALSE>>=
ex_fit4 <- ppm(ex_ppp ~ polynom(x, y, 4))
@
